Outbreak Threshold Detection

### 2023-03-03 notebooks/Julia/simulation-detection.qmd
Remove old ConstantJump simulation code as using Tau-Leaping

```{julia}
X = 800
Y = 20
Z = 800
u₀ = [X, Y, Z]
```

```{julia}
R₀ = 16
γ = 1/8
μ = 1 / (365 * 62.5)
β = R₀ * (γ + μ)
p = (β, γ, μ)
```

@@

```{julia}
u₀ = [800, 20, 800, NaN]
u₀[4] = sum(u₀[1:3])
R₀ = 16
γ = 1/8
μ = 20 / (365 * 62.5)
β = R₀ * (γ + μ)
p = (β, γ, μ)
prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Direct(), rj)
sol = solve(jump_prob, TauLeaping(); dt = δt)
sol_array = zeros(5, length(sol))
sol_array[1:4, :] = Array(sol)
sol_array[5, :] = sum(sol_array[1:3, :], dims = 1);

@@

```{julia}
infection_rate(u, p, t) = p[1] * u[1] * u[2] / (u[1] + u[2] + u[3])      # β*X*Y / N

function infection_affect!(integrator)
    integrator.u[1] -= 1         # X -> X - 1
    integrator.u[2] += 1         # Y -> Y + 1
    nothing
end

infection_jump = ConstantRateJump(infection_rate, infection_affect!)
```

```{julia}
recovery_rate(u, p, t) = p[2] * u[2]     # γ*Y

function recovery_affect!(integrator)
    integrator.u[2] -= 1        # Y -> Y - 1
    integrator.u[3] += 1        # Z -> Z + 1
    nothing
end

recovery_jump = ConstantRateJump(recovery_rate, recovery_affect!)
```

```{julia}
birth_rate(u, p, t) = p[3] * (u[1] + u[2] + u[3])        # μ * N

function birth_affect!(integrator)
    integrator.u[1] += 1
    # integrator.u[4] += 1
    nothing
end

birth_jump = ConstantRateJump(birth_rate, birth_affect!)
```

```{julia}
X_death_rate(u, p, t) = p[3] * u[1]       # μ * X

function X_death_affect!(integrator)
    integrator.u[1] -= 1
    nothing
end

X_death_jump = ConstantRateJump(X_death_rate, X_death_affect!)
```

```{julia}
Y_death_rate(u, p, t) = p[3] * u[2]       # μ * Y

function Y_death_affect!(integrator)
    integrator.u[2] -= 1
    nothing
end

Y_death_jump = ConstantRateJump(Y_death_rate, Y_death_affect!)
```

```{julia}
Z_death_rate(u, p, t) = p[3] * u[3]       # μ * R

function Z_death_affect!(integrator)
    integrator.u[3] -= 1
    nothing
end

Z_death_jump = ConstantRateJump(Z_death_rate, Z_death_affect!)
```

```{julia}
jumps = [infection_jump, recovery_jump, birth_jump, X_death_jump, Y_death_jump, Z_death_jump]
```

```{julia}
prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Direct(), jumps...)
sol = solve(jump_prob, SSAStepper())

sol_array = zeros(4, length(sol))
sol_array[1:4, :] = Array(sol)
sol_array[4, :] = sum(sol_array[1:3, :], dims = 1);
```
```{julia}
f = Figure()
ax = Axis(
    f[1, 1],
    xlabel = "Time",
    ylabel = "Number"
)

lines!(ax, sol.t, sol_array[1, :], linewidth = 3, label = "X(t)")
lines!(ax, sol.t, sol_array[2, :], linewidth = 3, label = "Y(t)")
lines!(ax, sol.t, sol_array[3, :], linewidth = 3, label = "Z(t)")
lines!(ax, sol.t, sol_array[4, :], linewidth = 3, label = "N(t)")

>>>>

@@

```{julia}
R₀ = 16
γ = 1/8
μ = 1 / (365 * 62.5)
β = R₀ * (γ + μ)
p = (β, γ, μ)

u₀ = [800, 20, 800, NaN]
u₀[4] = sum(u₀[1:3])
```

```{julia}
prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Direct(), rj)
sol = solve(jump_prob, TauLeaping(); dt = δt)
sol_array = zeros(5, length(sol))
sol_array[1:4, :] = Array(sol)
sol_array[5, :] = sum(sol_array[1:3, :], dims = 1);

@@
